\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\begin{document}

\begin{center}
  \LARGE\textbf{User Stories — Change of Major Workflow (v0.2)}\\[8pt]
  \large Team Project — User Management System
\end{center}

\bigskip
\section*{User Story 1}
As a \textbf{student}, I want to submit a \emph{Change of Major} form online so that I can request an official change of degree program without paper.

\medskip
\textbf{Acceptance Criteria:}
\begin{itemize}
  \item Student signs in with Office365.
  \item Student fields: current major, desired major, student ID auto-filled, date auto-filled.
  \item Student uploads signature image and submits form.
  \item System stores request and generates an initial PDF snapshot including the signature.
\end{itemize}

\bigskip
\section*{User Story 2}
As an \textbf{advisor}, I want to review the student request and either approve or return it with comments so that department administrative staff can complete the change.

\medskip
\textbf{Acceptance Criteria:}
\begin{itemize}
  \item Advisor sees all submitted fields and the signature.
  \item Advisor can Approve or Return with a comment.
  \item System saves a PDF snapshot of the advisor’s action.
\end{itemize}

\bigskip
\section*{User Story 3}
As a \textbf{department approver}, I want to finalize the approval and have the system produce a final signed PDF that the student can download.

\medskip
\textbf{Acceptance Criteria:}
\begin{itemize}
  \item System produces an archived PDF for each approval step.
  \item Final state changes to ``approved'' and is viewable by the student.
\end{itemize}

\end{document}
